%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{lipsum}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\name{Mahsa Moghaddass} % Your name
%\address{Apt # 206, 1420 Towers street, Montreal, QC \\ H3H 2E1} 
%\address{EV 13.119, 1455 de Maisonneuve Blvd. West, Montreal, Qc \\ H3G 1M8} 
\address {6 Eva road, Toronto, Ontario, Canada } 
\address{514-677-6548}
\address{mahsa.moghaddass@gmail.com} % Your phone number and email
\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Highlights of Qualifications}
{
\begin{itemize}
%Strong Data Analytics, Analytical Modeling, Data Visualization, and Machine Learning Skills.•Expert in Predictive Analytics, Designing Mathematical Optimization Models & Algorithms.
\item Strong in Data-Driven Optimization, Operations Research $\&$ Decision-Making Under Uncertainty.
\item Ability to Translate Raw Data into Business Insights Using Data Analytics $\&$ Visualization.
\item Expert in Predictive Analytics Using Machine Learning $\&$ Optimization Techniques.
%\item Experience in Recommender Systems to predict behavior $\&$ Improve Customers' Engagements. 
\item Highly Experienced in Recommender Systems (e.g., Predicting Customers Behaviors).
%\item Strong Data Analytics $\&$ Visualization Skills to Find Patterns $\&$ Trends in Python, Tableau. 
 \item Solid Knowledge and Experience in using C++, Python, SQL, Tableau, MS Office.
 %\item Experience in Recommender Systems to Improve Customer Engagemen
\item Strong Organizational, Interpersonal, Analytical $\&$ Problem Solving Skills.
%\item Strong Problem Solving Skills and Experience in Using Complex $\&$ Large Data Sets $\&$ PySpark.
%\item Strong Background in Production Planning Problems and Maintenance Strategies.
%\item Experience in Boosting Business profits $\&$ Customer Loyalty by increasing their Engagements. 
 \item Excellent Oral $\&$ Written Communication Skills in English and French.
 \item Ability to Work Both Independently $\&$ Collaboratively as an Effective Team Member.
\item Time $\&$ Detail Oriented, Highly Motivated, Quick-Learner, Self-Driven, Multi-Task $\&$ Energetic.
\end{itemize}
}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{WORK EXPERIENCE}
\begin{rSubsection}{Graduate Research Assistant, Data Analytics}{May 2016 - April 2020}{Data-Driven Operations Research Lab, Concordia University, Montreal, Canada}{ }
%\item Provided data cleaning, analytics and visualization using Python to find patterns and trends.
\item Designed mathematical optimization \& predictive models \& algorithms to solve complex problems.
%\item Implemented data analytics, preprocessing, visualization, and optimal data-driven decision making.
\item Worked with software \& packages in Python (pandas, seaborn, matplotlib, sklearn), MS Office.
\item Applied data-driven techniques to predict customers' behaviors and optimize their decisions.  
\item Provided optimal recommendations to help increase customer engagement and leverage business profits.
\item Worked with C++, Python, CPLEX (optimization software), Excel.
\end{rSubsection}
\begin{rSubsection}
{\bf  Instructor \& Teaching Assistant}{Sept 2016 - April 2020}{Concordia University, Montreal, Canada}{ }  
\item Teaching Operations Research, Production Planning, Manufacturing Systems \& Design, CPLEX.
\end{rSubsection}
\begin{rSubsection} {Data Analyst} {Jan 2015 - Feb 2016}{ KARPIRA International Recruitment Agency, Mashhad, Iran}{} \\
\item Provided data cleaning, analytics and visualization to recommend clients the
best services.
\item Communicated with suppliers and clients frequently to connect them in a best way.
\item Worked with SQL \& MS office.
\end{rSubsection}
\begin{rSubsection} {Business Analyst, Marketing Consultant} {Jan 2013 - Jan 2014}{ Grand Group Holding Company, Mashhad, Iran} {}
\item Provided marketing research \& campaign \& SWOT analysis for the company.
\item Interacted with market $\&$ clients to update the systems continuously.
\item Applied data visualization and analytics to provide business strategies.
\item Helped the company know their customers and demands well and provide services based on their needs.
\item Worked with SQL, MS Office \& CRM. 
\end{rSubsection}
%\begin{rSubsection}{Maintenance Analyst}{Sept 2011- Jan 2013}{Iran Khodro Automaker %Company, Mashhad, Iran }{Worked with maintenance strategies and business data to provide %the best strategies. }
%\end{rSubsection} 
 \end{rSection}
%--------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{VOLUNTEER EXPERIENCE}
\begin{rSubsection}{Mentorship Program Coordinator \& Leader}{June 2018-  Sept 2019}{Mechanical, Industrial $\&$ Aerospace Engineering Dept, Concordia University}{Montreal, Canada} 
    \item Coordinated seminars, managed teams and mentored first-year Ph.D. students in the department.
\item Organized high-level academic workshops, seminars, and events
\end{rSubsection}
 %\begin{rSubsection}{Student Academic Union Coordinator}{2007-2012}{Ferdowsi University}{Mashhad, Iran}  
  %   \item Organized high-level academic workshops and events \& english translator for Student Union.
%\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}
\begin{rSubsection}{Ph.D., Industrial Engineering (Operations Research), (GPA: 4.1/4.3)} {2016 -Mar 2020}{
 Gina Cody School of Engineering and Computer Science, Concordia University}{ Montreal, Canada}
\item  Thesis title: Inverse Integer Optimization With an Application in Recommender Systems.
\end{rSubsection}
\begin{rSubsection}{M.Sc, Industrial Management (Production), (GPA: 17.30/20)} { 2011 -- 2013} {Department of Economics and Business Administration,
    Ferdowsi University}{ Mashhad, Iran}
\item Thesis title: Optimization and Prioritization of Maintenance Strategies Using Interval AHP \& LP. 
\end{rSubsection}
\begin{rSubsection}{ B.Sc, Business Administration,  (GPA: 18.05/20)} { 2007 -- 2011}
 {Department of Economics and Business Administration, Ferdowsi University}{ Mashhad, Iran}

\end{rSubsection}
\end{rSection} 
 
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}
{\bf  Software Skills}  \\ 
% C++, Python, R, CPLEX, MS Office\\
C++, Python, SQL, CPLEX (optimization software), MS Office(Excel, PowerPoint), Tableau\\
%C++, Python, CPLEX, MS Office, R(intermediate) \\
 {\bf  Languages}  \\ 
{English , French (level: B2)} 
\end{rSection}

% Awards
%----------------------------------------------------------------------------------------
\begin{rSection}{AWARDS \& HONORS}
{\bf Concordia University Accelerator Award } \hfill {\em Aug 2019} \\ 
%\textit{Concordia University} \hfill {\em Montreal, Canada}\\
{\bf Concordia University Conference and Exposition Award} \hfill {\em May 2019 $\&$  May 2018} \\ 
%Concordia University \hfill {\em Montreal, Canada}\\
{\bf Concordia University Best Industrial Engineering Ph.D. Poster Award} \hfill {\em April 2019} \\  
{\bf  Canadian Operational Research Society (CORS) Graduate Funding Award} \hfill {\em June 2018} \\ 
 \textit{CORS Annual Conference} \hfill {\em Halifax, Canada}\\
%\textit{Concordia University} \hfill {\em Montreal, Canada}\\
{\bf  Concordia University International Tuition Award of Excellence} \hfill {\em Aug 2019} \\ 
%\textit{Concordia University} \hfill {\em Montreal, Canada}\\
%{\bf Top-Ranked Student Among 30 Graduate Students in Master's Study} \hfill {\em  Jan 2013} \\ 
%Ferdowsi University \hfill {\em Mashhad, Iran}\\
{\bf Eligible to Pursue Master's Study Without Entrance Exam} (Outstanding Student) \hfill {\em  Jan 2011} \\ 
\textit{Ferdowsi University} \hfill {\em Mashhad, Iran}
\end{rSection} 
%----------------------------------------------------------------------------------------
%PAPER----------------------------------------------------------------------------------------
\begin{rSection}{Journals}
  {\bf Data-Driven Inverse Optimization for Recommender Systems} \& \\ 
   {\bf   Inverse Integer Optimization with Multiple Observations} \\ 
  \textit{M. Moghaddass and D. Terekhov, Under review at Optimization Letters Journal}  \\
 {\bf  Inverse Integer Optimization with an Imperfect  Observation}  \\ 
 \textit{M. Moghaddass and D. Terekhov, Under second review at Operations Research Letters Journal}  
\end{rSection}
%----------------------------------------------------------------------------------------
% Workshops
%----------------------------------------------------------------------------------------
\begin{rSection}{Workshops \& Certificates}
 {\bf Python for Data Science and Machine Learning BootCamp } \hfill {\em Jan 2020} \\ 
\textit{UDEMY online course, (NumPy, Pandas, Seaborn, Matplotlib, Plotly, Scikit-Learn, Machine Learning)}\hfill \\
 {\bf Tableau Training For Data Science} \hfill {\em June 2020} \\ 
\textit{UDEMY online course, (Data visualisation skills)}\hfill \\
 {\bf Workshop on Recommender Systems } \hfill {\em Aug 2019} \\ 
\textit{IVADO, HEC Montreal, Canada (Learning recommender systems and Algorithms in Python)}\hfill  
%{\bf CPLEX Training School }\hfill {\em June 2017} \\
%\textit{Concordia University, Montreal, Canada (Learning CPLEX)}\hfill \\
%{\bf Mixed Integer Programming Workshop}\hfill {\em Jun 2017} \\
%\textit{HEC Montreal, Canada}\hfill 
 
\end{rSection} 
%----------------------------------------------------------------------------------------

% Workshops 
%----------------------------------------------------------------------------------------
%\begin{rSection}{References}
%References available upon request
%\end{rSection} 
 
\end{document}
